mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-21 EMSOFT2016/thesis.tex
update

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as worst-execution time and response time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

@@

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multipel tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.

@@

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{url:ASP}.

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
%Therefore, the design can send the bytecode faster.
In addition, the design can save the time to connect a storage/ROM device to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
The overhead of multitask is about 5 \% ($(multitask-singletask)/multitask$).
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheuler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than 10 msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
Each execution time of cyclic period is the same as the others.
That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
(B) is not modified, and can be utilized regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
        \multicolumn{3}{l}{  }\\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
Component-based development can increase productivity and decrease complexity.

>>>>

\begin{document}
\maketitle
\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\section{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

Although script languages are easy to use and read, their execution time are slower than C language's.
For embedded systems, the real-time properties such as estimation of worst-execution time are very important factors.
Therefore, it is difficult to apply the script languages to embedded systems.

@@

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication because a common part of software is regarded as a component.

@@

As the target RTOS, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is used in this paper.
TOPPERS/HRP2 is an RTOS based on $\mu$ITRON \cite{par:microITRON} with memory protection.
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/ASP \cite{par:ASP}, \cite{url:ASP}.

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
%Therefore, the design can send the bytecode faster.
In addition, the design can save the time to rewrite a storage/ROM device, and to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheuler practically because the overhead of the RiteVM scheuler is about 5 \%.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheuler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than eight msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
%Each execution time of cyclic period is the same as the others.
%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
The execution time decreases as the cyclic time become larger, because the number of switching tasks decreases.
The execution time of one msec is only about 1 \% lager than that of eight msec.
The RiteVM scheuler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
%This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
%The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillfull component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
Component-based development can increase productivity.

### 2016-02-21 thesis/thesis.tex
update

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a strage device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}
\chapter{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

\section{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease complexity and difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication  because a common part of software is regarded as a component.

>>>>

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}
\chapter{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

\section{TECS}
\label{sec:TECS}
TECS (TOPPERS Embedded Component System) is a component system suitable for embedded systems.
TECS helps decrease difficulty because the generated component diagram can visualize the structure of whole software.
It can also help increase productivity and reduce development duplication because a common part of software is regarded as a component.
